%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% IMPORTANT: Run XeLaTex on it, not regular Latex
\documentclass[]{deedy-resume}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%d\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{}{Vadim Eisenberg}{%
  Software Developer, M.Sc. in Computer Science, hands-on, broad knowledge%
  }{%
    \href{mailto:Vadim.Eisenberg@gmail.com}{Vadim.Eisenberg@gmail.com}
  | +972-54-7993919%
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Technion - IIT}
\descript{M. Sc. in Computer Science}
\location{2007-2012 | Haifa, Israel}
\sectionsep
\subsection{Technion - IIT}
\descript{B. Sc. in Computer Science}
\location{1996-2000 | Haifa, Israel}
GPA 90 (cum laude)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROFESSIONAL SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
Software Engineering and Architecture \textbullet{} Programming Languages \textbullet{} Software Design \textbullet{} Design Patterns \textbullet{} Application Frameworks/Middleware \textbullet{} Semantic Web and Database technologies \textbullet{} Mobile and Web applications \textbullet{} Microservices and Service Meshes
\sectionsep

\subsection{Programming}
Java \textbullet{} Go \textbullet{} JavaScript \textbullet{} Swift \textbullet{} C\\
C++ \textbullet{} Ruby  \textbullet{}  Bash \textbullet{}  Assembly
\sectionsep

\subsection{Environments}
Unix \textbullet{}  Android \textbullet{}  Node.js \\
Ruby on Rails \textbullet{} Server-Side Swift \\
Kubernetes
\sectionsep

\subsection{Favorite Tools}
Git \textbullet{}  Make \textbullet{}  Bash \textbullet{} \\
GitHub ecosystem: code analysis, code coverage, continuous integration
\sectionsep

\section{Languages}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
English (bilingual) \textbullet{} Hebrew (bilingual) \\
Russian (native)  \textbullet{} Polish (limited working) \\
German (limited working)
\sectionsep

% VERTICAL ALIGNMENT
\sectionsep
% VERTICAL ALIGNMENT

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     BLOGS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Blogs}
\href{https://istio.io/search.html?q=vadim\%20eisenberg}{posts at istio.io} \\
\href{http://vadimeisenberg.blogspot.com}{vadimeisenberg.blogspot.com}
\sectionsep

% VERTICAL ALIGNMENT
\sectionsep
% VERTICAL ALIGNMENT

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MISC
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MISC}
Marathon time: 3:42:15

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{IBM Research}
\descript{| IoT Technologies group}
\location{2013--2022 | Haifa, Israel}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Development of \href{https://github.com/stolostron/hub-of-hubs}{Hub-of-Hubs prototype for Red Hat Advanced Cluster Management for Kubernetes}. Three orders of magnitude scalability improvement.
\item Development of \href{https://istio.io}{Istio Service Mesh}, ingress/egress traffic control, multi-cluster/multi-mesh.
Contributor \href{https://github.com/istio/istio/graphs/contributors}{\#45} to \href{https://github.com/istio/istio}{istio/istio}, \href{https://github.com/istio/istio.io/graphs/contributors}{\#8} to \href{https://github.com/istio/istio.io}{istio/istio.io}. Consulting a large enterprise on their Istio adoption.
\item Development of \href{https://github.com/Kitura/Kitura}{Kitura - a Swift web framework}. Contributor \href{https://github.com/IBM-Swift/Kitura/graphs/contributors}{\#1}.
\item Development of Data and Service Layers of IBM MobileFirst iOS apps.
\item Development of IBM \href{https://heidloff.net/article/ibm-announces-citizen-developer-tool-to-build-situational-apps-bluemix-rapidapps/}{Rapid Apps}.
\item Integration of IBM BPM and IBM Worklight.
\end{tightemize}
\sectionsep

\runsubsection{IBM Research}
\descript{| Healthcare and Life Sciences group}
\location{2010--2012 | Haifa, Israel}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \href{https://cordis.europa.eu/project/id/247950}{universAAL project}. Development of a distributed platform for Ambient Assisted Living applications.
\item Various data processing and healthcare products projects.
\end{tightemize}
\sectionsep

\runsubsection{Technion - Israel Insitute of Technology} \\
\descript{Computer Science department}
\location{2007--2009 | Haifa, Israel}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Teaching Assistant for the course \textit{Introduction to Systems Programming}, \href{https://ugportal.net.technion.ac.il/files/2014/05/horev-tashasa.pdf}{Excellent TA award}
\sectionsep

\runsubsection{IBM Research} \\
\descript{Performance Analysis and Optimization Technologies group}
\location{1998--2007 | Haifa, Israel}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item 2003--2007 Developer and Project Leader. Design and development of FDPR-Pro, a multiplatform feedback-based post-link optimization tool.
\item  1998--2002 Part time position (student). Development of FDPR and FDPR-Pro post-link optimization tools.
\end{tightemize}
\sectionsep

% VERTICAL ALIGNMENT
%\sectionsep
% VERTICAL ALIGNMENT

\section{PERSONALITY}
Passionate about Software Development \textbullet{} Dedicated to execution\\
Quick learner \textbullet{} Marathon runner\\
Flexible team player \textbullet{} Teacher \textbullet{}  Able to work under pressure \textbullet{} Hands-on\\
Team Leader \textbullet{} Creative Problem Solver \textbullet{} Blogger

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links}
LinkedIn:  \href{https://www.linkedin.com/in/vadimeisenberg}{vadimeisenberg} \\
GitHub: \href{https://github.com/vadimeisenberg}{vadimeisenberg} \\
Previous GitHub (IBM): \href{https://github.com/vadimeisenbergibm}{vadimeisenbergibm} \\
StackOverflow: \href{http://stackoverflow.com/users/553720/vadim-eisenberg}{553720/vadim-eisenberg}, reputation 3207 \\
Twitter: \href{https://twitter.com/VadimEisenberg}{VadimEisenberg} \\
DBLP: \href{http://dblp.uni-trier.de/pers/hd/e/Eisenberg:Vadim}{http://dblp.uni-trier.de/pers/hd/e/Eisenberg:Vadim} \\
This resume: \href{https://github.com/VadimEisenberg/resume/raw/gh-pages/resume.pdf}{resume.pdf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%     Other
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{Other}
%
%\runsubsection{Zimm's Yard Services}
%\descript{| Owner}
%\location{May 2008 – Aug 2013 | New Berlin, WI}
%\begin{tightemize}
%\item Started neighborhood lawn service business, ran for five summers
%\item Developed \custombold{Java} app to track transactions, create invoices,
%  etc.
%\end{tightemize}
%\sectionsep

%\runsubsection{SDNB Tech Dept}
%\descript{| Intern }
%\location{Jun 2013 – Aug 2013 | New Berlin, WI}
%\begin{tightemize}
%\item Aided with common IT-related tasks, such as batch OS imaging \& BIOS editing
%\item Provided technical and troubleshooting support for faculty and staff
%\end{tightemize}
%\sectionsep

%\runsubsection{Kumon Learning Center}
%\descript{| Math and Reading Tutor}
%\location{Oct 2011 – Aug 2013 | Franklin, WI}
%\begin{tightemize}
%\item Tutored math and reading one-on-one with students aged pre-K to high school
%\end{tightemize}
%\sectionsep

%\runsubsection{Spanish Language Interpreter}
%\descript{| Ebenezer Food Pantry}
%\location{2009 - 2013 | Milwaukee, WI}
%\sectionsep
%\runsubsection{Student Tech Speaker}
%\descript{| Bring Your Own Device Talk Series}
%\location{2012 - 2013| Wisconsin}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% NOTE: These are not mine. They are remnants from the template.
%  \section{Awards}
%  \begin{tabular}{rll}
%  2014	     & top 52/2500  & KPCB Engineering Fellow\\
%  2014	     & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
%  2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
%  2013	     & National  & Jump Trading Challenge Finalist\\
%  2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
%  2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%  2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%  2010     & National & Comp. Soc. of India's National Programming Contest\\
%  \end{tabular}
%  \sectionsep
%
%  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  %     SOCIETIES
%  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  \section{Societies}
%
%  \begin{tabular}{rll}
%  2014 	& top 12\%ile    & Tau Beta Pi Engineering Honor Society\\
%  2014   & National   & The Global Leadership and Education Forum (tGELF)\\
%  2012   &  National  & Golden Key International Honor Society\\
%  2012   &  National   & National Society of Collegiate Scholars\\
%  \end{tabular}
%  \sectionsep
%
\end{minipage}
\end{document}  \documentclass[]{article}
